### 2018-04-12 4_input.tex
add today's released changes.

the old input language syntax

new one iwth changes highlighted

>>>>

The \Porthos tool used a small subset of C as an input language as described on Figure~\ref{syntax:porthos}\cite{Porthos17}:

\begin{figure}[H]
\begin{lstlisting}[mathescape=true,
        caption={Syntax of an input language of \Porthos},
        captionpos=b,
        label={syntax:porthos},
        basicstyle=\ttfamily\footnotesize,
        keywordstyle=\bfseries,
        literate={<--}{$\leftarrow{}$}{1},%{::=}{???},%:\!:\!=},
        morekeywords={if,then,else,return,while,program,thread,mfence,sync,lwsync,isync}]
<prog>  : program <thrd>*
<thrd>  : thread <tid> <inst>
<inst>  : <atom> 
        | <inst> ; <inst>
        | while <pred> <inst>
        | if <pred > then <inst> else <inst>
<atom>  : <reg> <-- <exp> 
        | <reg> <-- <loc>
        | <loc> := <reg> 
        | mfence
        | sync
        | lwsync
        | isync
\end{lstlisting}
%\caption={Syntax of an input language of \Porthos}
%\label={syntax:porthos}
\end{figure}

// todo: old syntax more precisely

The input language of \Porthos supported recursive definitions of control-flow instructions, which needed to be extended to support arbitrary jumps expressible in C. Also, for the purpose of simplicity, all kinds of fence instructions and different types of variable assignments (shared variable assignment `\texttt{:=}' or local variable assignment `$\mathtt{\rightarrow}$') were defined directly in the grammar for \Porthos, whereas the semantics of function invocations need to be determined dynamically during the interpretation
% according to the set of known functions
(see Chapter~\ref{???}).

//todo: new syntax

### 2018-04-12 5_impl.tex
Complete the data-flow encoding.
Rename; changes from bus.
add today's released changes.

\chapter{Implementation}
\label{ch:impl}

This chapter describes the architecture of the tool \texttt{mousquitaires} ...

@@

% why: https://stackoverflow.com/a/13968707/4977823

\section{Program Requirements}
\label{ch:impl:requirements}

- stability (tests)

- scalability (new features of language, new models, new tasks for a program )

- transparency

- efficiency

\section{Program Components}
\label{ch:impl:comp}
Big view

\section{C11 to YTree parser}
\label{ch:impl:ytree}

>>>>

\chapter{\nohyphens{The~\mousquetaires:~implementation}}
\label{ch:impl}

This Chapter describes the architecture of the tool \mousquetaires.

@@

% why not AST: https://stackoverflow.com/a/13968707/4977823

\section{Requirements}
\label{ch:impl:requirements}

The main reason for starting the work on re-implementing the \Porthos tool was the need to extend input language to be able to process real C programs in perspective.

The target requirements for the new tool was set up as following (in descending order of priority):

\begin{enumerate}
        \item stability and transparency (KISS principle)
                \begin{itemize}
                        \item choice in favour of simplicity and readability at every step;
                        \item usage of software design patterns if necessary;
                        \item usage of immutable data structures for intermediate representations;
                        \item high code coverage of unit and functional tests;
                \end{itemize}                
        \item efficiency
                \begin{itemize}
                        %\item usage of time- and memory-optimised data structures;
                        \item keeping the trade-off between execution time and memory consumption;
                \end{itemize}
        \item extensibility
                \begin{itemize}
                        \item clear modular architecture
                \end{itemize}
\end{enumerate}

\section{Program Components}
\label{ch:impl:comp}

Generally, \mousquetaires uses following

\section{Parsing the input language as YTree}
\label{ch:impl:ytree}
